%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% MCM/ICM LaTeX Template %%
%% MCM/ICM                           %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\documentclass{mcmthesis}
%\usepackage{geometry}
%\geometry{left=1in,right=0.75in,top=1in,bottom=1in}
\documentclass{mcmthesis}
\mcmsetup{CTeX = false,  
	tcn = 2616842, problem = X,
	sheet = true, titleinsheet = true, keywordsinsheet = true,
	titlepage = false, abstract = true}
\usepackage{newtxtext}%\usepackage{palatino}
\usepackage{lipsum}
\usepackage{float}
\usepackage{indentfirst}
\usepackage{multirow}
\setlength{\parindent}{1em}
\title{TITLE:\\ SUB-TITLE}   

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
	
	%%%%%%%%%%% Begin Summary %%%%%%%%%%%
	% Enter your summary here replacing the (red) text
	% Replace the text from here ...
	\begin{abstract}
		This is the abstract!
		\begin{keywords}
			Keywords Here.
		\end{keywords}
	\end{abstract}

\maketitle
% to here
%%%%%%%%%%% End Summary %%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\clearpage
\pagestyle{fancy}
% Uncomment the next line to generate a Table of Contents
%\tableofcontents 
\newpage
\setcounter{page}{1}
\rhead{Page \thepage\ }
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage   %%目录页
\tableofcontents
\thispagestyle{empty}
\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\subsection{Problem Background}
	PROBLEM BACKGROUND
\subsection{Restatement of the Problem}
	RESTATEMENT
\subsection{Our Work}
	ONE FIGURE AND SOME DISCRIPTION.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Assumptions and Notations}
\subsection{Assumptions}
	\begin{itemize}
		\item
		\item
		\item
		\item
	\end{itemize}
\subsection{Notations}
	NOTATIONS 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Model I: XXXXXX}
	PRE-DISCRIPTION OF THE MODEL. SOME FIGURES AS WELL.
\subsection{Factors/Development of the model}
	BALABALA
\subsubsection{More Sub-details I}
	BALABALA
\subsubsection{More Sub-details II}
	BALABALA
\subsection{Factors/Development of the model}
	BALABALA
\subsection{Factors/Development of the model}
	BALABALA

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Model II: XXXXXX}
	PRE-DISCRIPTION OF THE MODEL. SOME FIGURES AS WELL.
\subsection{Factors/Development of the model}
	BALABALA
\subsubsection{More Sub-details I}
	BALABALA
\subsubsection{More Sub-details II}
	BALABALA
\subsection{Factors/Development of the model}
	BALABALA
\subsection{Factors/Development of the model}
	BALABALA

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Application of Models}
	CHOOSE CERTAIN REGION TO UTILIZE THE MODELS ABOVE.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Sensitivity Analysis}
	NECESSARY SENSITIVITY ANALYSIS HERE.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Model Evaluation and Further Discussion}
\subsection{Strengths}
	\begin{itemize}
		\item
		\item
		\item
		\item
	\end{itemize}
\subsection{Weakness}
	\begin{itemize}
		\item
		\item
	\end{itemize}
\subsection{Further Discussion}
	\begin{itemize}
		\item
		\item
	\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Newspaper Artical/Flyer/Magazine}
	BALABALA

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\newpage
\begin{thebibliography}{99}
	\bibitem{1} 
	\bibitem{2}
	\bibitem{3}
	\bibitem{4}
	\bibitem{5}
	\bibitem{6}
	\bibitem{7}
	\bibitem{8}
	\bibitem{9}
	\bibitem{10}
	\bibitem{11}
	\bibitem{12}
	\bibitem{13}
\end{thebibliography}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\newpage

\newpage
\newpage
\begin{appendices}
\section{First appendix}
	\begin{lstlisting}
		CODE1
		2
		3
		4
		5
	\end{lstlisting}
\end{appendices}

\end{document}
\end
